Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-14 inst/examples/20170201-manuscript.Rmd
updateing analyses

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
# Analysis time window
df <- df0 %>% filter(publication_year >= 1640 & publication_year <= 1911) %>%
              group_by(publication_decade) %>%
              summarize(mean_title_length = mean(title_length_wordcount),
	      		n = n())

for (catal in unique(df$catalog)) {
  dfs <- subset(df, catalog == catal)
  p <- ggplot(dfs, aes(x = publication_decade, y = mean_title_length)) +
       geom_point(aes(size = n), size = 5) +
       geom_line(size = 1) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle(paste("Title length (", catal, ")", sep = ""))

@@

  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))

  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  #cols <- c("white", "Purple", "yellow", "orange", "darkgray")
  cols <- c("white", "lightgray", "gray", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
  rectangles$shade <- factor(rectangles$shade)

@@

               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772

@@

  rectangles$shade <- rep(c("Background", "Highlight"),
  		          length = nrow(rectangles))

  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  cols <- c("white", "gray", "darkgray")
  rectangles$place <- rectangles$shade
  rectangles$place[rectangles$place == "Highlight"] <- riksplace
  rectangles$place[rectangles$place == "Background"] <- "" 
  rectangles$shade <- factor(rectangles$shade)

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
         scale_fill_manual(values = cols) +
	 guides(fill = "none")

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_brewer(palette="Greys") +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)       
       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))

@@

With percentage of all books that were not published by the printing house of the court.

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     xlab("Publication year") +
     ylab("Title count")

@@

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place")) 
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype= guide_legend(title = "Place"))        
print(p)
```

>>>>

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
# Analysis time window
df <- df0 %>% filter(publication_year >= 1640 & publication_year <= 1911) %>%
              group_by(catalog, publication_decade) %>%
              summarize(mean_title_length = mean(title_length_wordcount),
	      		n = n())

for (catal in unique(df$catalog)) {
  dfs <- subset(df, catalog == catal)
  p <- ggplot(dfs, aes(x = publication_decade, y = mean_title_length)) +
       geom_point(aes(size = n), size = 5) +
       geom_line(size = 1) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle(paste("Mean title length (", catal, ")", sep = ""))

@@

  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  #cols <- c("white", "Purple", "yellow", "orange", "darkgray")
  cols <- c("white", "lightgray", "gray", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
  rectangles$shade <- factor(rectangles$shade)

@@

@@

  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  cols <- c("white", "lightgray", "gray", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
  rectangles$shade <- factor(rectangles$shade)

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
         scale_fill_brewer(palette="Greys") +
	 guides(fill = "none")

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_brewer(palette="Greys") +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)       
       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))

@@

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
     xlab("Publication year") +
     ylab("Title count")

@@

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place")) 
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Publication year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       scale_fill_manual(values = c("darkgray", "black")) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
